The human in the loop: volunteer computing as a socio-technical system

### 2016-02-29 Alife16/paper.tex
Adding all new graphs.
For comparison. Changed GEV to Weibull. Please @unintendedbear @fergunet @mariosky Do something! Check for typos, inconsistencies, and so on..

Still some stuff to go, comparison with the new cache and general conclusions.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-4.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-24.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-7-31.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=128.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=64.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=32.png}
\caption{Number of {\tt PUT}s per unique IP and fit to a Generalized
  Extreme Value distribution (in red). From left to right, experiments
  4/4, 4/24 and 7/31.} 
% Plotted with ../data/plot-zipf-openshift.R
\label{fig:puts:os}
\end{figure}
%
 This exponential distribution also appears in the
distribution of HTTP {\tt PUT}s, equivalent to the number of
generations divided by 100, contributed by every user, which is shown
in Figure \ref{fig:puts:os}. These results show a Zipf-like behavior,
so we have fitted it to the Generalized Extreme Value distribution,
with the resulting parameters shown in Table \ref{tab:puts:os}.
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value distribution of
  the number of {\tt PUT}s per unique IP. \label{tab:puts:os}}
\begin{center}
\begin{tabular}{l|ccc}
\hline
Date  & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
4/4 &  8.541 $\pm$ 1.0926  & 12.442 $\pm$ 1.7302 &  1.388 $\pm$
0.1377 \\
4/24 & 6.148 $\pm$ 0.3782 & 7.354 $\pm$ 0.5105 & 1.090 $\pm$  0.0697  \\
7/31 & 11.645 $\pm$ 1.475 & 16.365 $\pm$ 2.201 &  1.265 $\pm$ 0.132   \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
This distribution was originally proposed to fit extreme values
\citep{resnick2013extreme} and contains, as a special case, the inverse
Weibull distribution which was fitted to volunteer computing
frameworks such as SETI@home \citep{javadi2009mining}. We obviously do
not pretend to compare our system in scale or complexity with it, but
to point out that the behavior of volunteer computing nodes follows a
certain pattern, found in SETI@home, and which also appears in our system. This
distribution is governed by three parameters, the usual location $\mu$
which is related to where it has its {\em center} and a scale $\sigma$,
related to the size, but also a third shape $\xi$ parameter that is
related to its skewness, that is, how skewed it is around the central
location. Positive parameters indicate that the distribution {\em
  leans} towards the origin, and negative ones towards the other extreme
value. In this case, Table \ref{tab:puts:os} shows $\xi$ values
greater than one and between one and 1.4, which indicates that the
three experiments share this origin-leaning pattern, with many users
donating a few cycles and just a few donating extreme values. Random
distributions with these parameters have been plotted in red in
Figure \ref{fig:puts:os}, indicating that the fit is good enough. The
predictive value of these fits, however, is limited, over all taking
into account the low correlation between successive events shown
above.

@@

This work has been supported in part by TIN2011-28627-C04-02 and
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
PROY-PP2015-06 (Plan Propio 2015 UGR),  % please, remember to include all the current projects   ;)   Thanks!
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico) and PYR-2014-17
GENIL project (CEI-BIOTIC Granada). We would also like to thank the
anonymous reviewers of previous versions of this paper who have really
helped us to improve 
this paper (and our work) with their suggestions. We are also grateful
to Anna S\'aez de Tejada for her help with the data processing
scripts. We are also grateful to {\tt @otisdriftwood} for his help
gathering users for the new experiments.

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-4.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-24.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-7-31.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=128.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=64.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=32.png}
\caption{Number of {\tt PUT}s per unique IP and fit to a Weibull
  distribution (in red). From left to right and top to bottom, experiments
  4/4, 4/24 and 7/31 and new experiments with cache=128, 64, 32.} 
% Plotted with ../data/plot-zipf-openshift.R
\label{fig:puts:os}
\end{figure}
%
 This exponential distribution also appears in the
distribution of HTTP {\tt PUT}s, equivalent to the number of
generations divided by 100, contributed by every user, which is shown
in Figure \ref{fig:puts:os}. These results show a Zipf-like behavior,
so we have fitted it to the Generalized Extreme Value distribution,
with the resulting parameters shown in Table \ref{tab:puts:os}.
%
\begin{table}
\caption{Summary of fit to Generalized Extreme Value distribution of
  the number of {\tt PUT}s per unique IP. \label{tab:puts:os}}
\begin{center}
\begin{tabular}{l|ccc}
\hline
Date  & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
4/4 &  8.541 $\pm$ 1.0926  & 12.442 $\pm$ 1.7302 &  1.388 $\pm$
0.1377 \\
4/24 & 6.148 $\pm$ 0.3782 & 7.354 $\pm$ 0.5105 & 1.090 $\pm$  0.0697  \\
7/31 & 11.645 $\pm$ 1.475 & 16.365 $\pm$ 2.201 &  1.265 $\pm$ 0.132   \\
\hline
\end{tabular}
\end{center}
\end{table}
%
This distribution was originally proposed to fit extreme values
\citep{resnick2013extreme} and contains, as a special case, the inverse
Weibull distribution which was fitted to volunteer computing
frameworks such as SETI@home \citep{javadi2009mining}. We obviously do
not pretend to compare our system in scale or complexity with it, but
to point out that the behavior of volunteer computing nodes follows a
certain pattern, found in SETI@home, and which also appears in our system. This
distribution is governed by three parameters, the usual location $\mu$
which is related to where it has its {\em center} and a scale $\sigma$,
related to the size, but also a third shape $\xi$ parameter that is
related to its skewness, that is, how skewed it is around the central
location. Positive parameters indicate that the distribution {\em
  leans} towards the origin, and negative ones towards the other extreme
value. In this case, Table \ref{tab:puts:os} shows $\xi$ values
greater than one and between one and 1.4, which indicates that the
three experiments share this origin-leaning pattern, with many users
donating a few cycles and just a few donating extreme values. Random
distributions with these parameters have been plotted in red in
Figure \ref{fig:puts:os}, indicating that the fit is good enough. The
predictive value of these fits, however, is limited, over all taking
into account the low correlation between successive events shown
above.

@@

This work has been supported in part by TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
PROY-PP2015-06 (Plan Propio 2015 UGR)  % please, remember to include all the current projects   ;)   Thanks!
. We would also like to thank the
anonymous reviewers of previous versions of this paper who have really
helped us to improve 
this paper (and our work) with their suggestions. We are also grateful
to Anna S\'aez de Tejada for her help with the data processing
scripts. We are also grateful to {\tt @otisdriftwood} for his help
gathering users for the new experiments.
